The Multi-Stencil Framework: A Component-Based Approach to Orchestrate Stencils

### 2017-03-06 ARTICLES/IJPP/articleR1/conclusion.tex
passe conclu

In this paper, we have presented the Multi-Stencil Framework. MSF is built upon a meta-model of a multi-stencil program which has been presented in Section~\ref{sect:formalism}. From this meta-model has been designed, first, the generic component assembly of a multi-stencil program, and second, the domain specific language MSL that enables the description of a specific application by a numerician. From these entries, the MSF compiler, namely MSC, is able to generate automatically a parallel specific assembly of the simulation. This specific assembly represents the parallel orchestration of computations, independently of implementation choices. Moreover, by combining a meta-model and component-based programming models MSF has the particularity to enhance separation of concerns and code-reuse of existing solutions (\eg SkelGIS and OpenMP in this paper). Finally, MSF has been evaluated on the real case simulation FullSWOF2D. Results have shown that even if component models have been used, strong and weak scalings of MSF (for its data parallelization technique) do not suffer from overheads. Results have also shown that the hybrid parallelization handled by MSF could increase performances when MPI communications are too heavy, which is a new contribution compared to existing solutions. Finally, we have presented evaluations on fusion optimization that demonstrates that fusion is not always a good choice, particularly when performing hybrid parallelism.

@@

The same choice problem is raised by fusion evaluations of Section~\ref{sect:fus}. Actually, fusion optimization is not always relevant. Thus, for the same reasons than parallelization techniques, an actor algorithm could choose the best solution for a given execution. To design such actor algorithms different solutions should be studied, such as following an approximated behavior model, or using calibration runs to then use deep learning algorithms etc.

>>>>

In this paper, we have presented MSF, the multi-stencil framework.
MSF is built upon a meta-model of a multi-stencil program which we have presented in Section~\ref{sect:formalism}.
From this meta-model, we have designed, first, the generic component assembly of a multi-stencil program, and second, the domain specific language MSL that enables the description of a specific application by a numerician.
From these entries, MSC, the MSF compiler, automatically generates a parallel component assembly.
This assembly represents the parallel orchestration of computations, independently of implementation choices.

By combining a meta-model and component-based programming, MSF has the particularity to enhance separation of concerns and code-reuse of existing solutions (\eg SkelGIS and OpenMP in this paper).
MSF has been evaluated on the real case simulation FullSWOF2D.
Results show that the MSF runtime does not induce unwanted overheads for its data parallelization technique on both strong and weak scalings.
Results also show that the hybrid parallelization supported by MSF can increase performance when the data parallelism exposed by the simulation is not enough, which is a new contribution compared to existing solutions.
Finally, we have evaluated the fusion optimization and shown that it often increases performance but is not always a good choice, particularly when performing hybrid parallelism.

@@

The same choice problem is raised by the fusion optimization. For the same reasons as for parallelization techniques, an actor algorithm could choose the best solution for a given execution. To design such actor algorithms different solutions should be studied, such as following an approximated behavior model, or using calibration runs to then use deep learning algorithms, etc.
